Online {\IterComp}

### 2017-11-13 motivation.tex
updates to the motivation section.

    \paragraph{Iterative compilation needs representative inputs.} \FIXME{Fig.XXX} shows what happens when we apply iterative compilation
    on \FIXME{susan\_c} using the wrong inputs. We selected \FIXME{50} of the 1,000 inputs of \textit{KDataSets}~\cite{chen10,chen12a} for
    \FIXME{susan\_c} and we used them to evaluate different optimizations. The red bars show the average speedup over \texttt{-O3} achieved
    by the optimization sequence selected by iterative compilation. On the left is the average over the \FIXME{50} inputs, on the right the
    average over all 1,000 inputs. The selected sequence works great for the inputs we used, but it fails miserably for the rest, slowing
    down the benchmark by \FIXME{5\%} on average.

    The blue bars, on the other hand, show the ideal case where good optimizations are selected based on their average effect on all
    inputs, not just a subset. Not only is the average speedup over all 1,000 inputs considerable, \FIXME{13\%} over \texttt{-O3}, but it
    also works well for the \FIXME{50} input subset. The speedup for the subset is only \FIXME{1\%} less of what we got when we optimized
    specifically for that subset.

    Making iterative compilation work in this example is not a matter of handling input sensitivity, we were able to find an optimization
    sequence that works well both on average and under most inputs. It is a matter of finding a set of inputs that represents the full
    range of inputs the application is likely to process. If we do, we can improve average performance by \FIXME{13\%}. If not, we might
    hurt average performance instead.

@@

    \paragraph{Using real inputs online is not enough.} We could overcome these problems by just evaluating optimization sequences online
    while the application is being used. This gives us live data but creates a new problem. Optimizations sequences are compared based on
    how much faster the program becomes. When all of them are tested against the same inputs, it is just a matter of comparing runtimes.
    A shorter runtime for processing the same data means a more efficient binary. With live data, we cannot do this, each binary processes
    whatever the input happens to be. We need another efficiency metric that only requires a single use of an optimized binary with a
    single input.

>>>>

    \paragraph{Iterative compilation needs representative inputs.} 
    In order to highlight what happens when we apply iterative compilation using the wrong set of inputs, we selected two distinct sets of
    10 out of the 1,000 inputs of the of \textit{KDataSets}~\cite{chen10,chen12a} for the \texttt{tiff2bw} benchmark.
    The first set represents the training set, i.e., the set of inputs that will be used for selecting the best optimization sequence by
    iterative compilation, and the second set is a specific set of inputs which is misrepresented by the training set.
    After performing iterative compilation on the first set, the selected optimization sequence has an average speedup of 1.22 over -O3 for
    the training set itself, but it produces a slowdown of 0.91 for the second set of inputs.
    However, if the iterative compilation was performed on the second set itself, it would be able to find a optimization sequence that
    produces a speedup of \FIXME{1.02} over -O3.

    %Even with larger set of training inputs, the lack of representative inputs for iterative compilation can still hurt performance.
    %For the same \textttt{tiff2bw} benchmark, we were able to partition the whole dataset into 
    %I.C. on 85% set has speedup 1.06 on the set itself and 0.975 slowdown on the 15% set.
    %I.C. on 15% set has speedup 1.03.

%%    \paragraph{Iterative compilation needs representative inputs.} \FIXME{Fig.XXX} shows what happens when we apply iterative compilation
%%    on \FIXME{susan\_c} using the wrong inputs. We selected \FIXME{50} of the 1,000 inputs of \textit{KDataSets}~\cite{chen10,chen12a} for
%%    \FIXME{susan\_c} and we used them to evaluate different optimizations. The red bars show the average speedup over \texttt{-O3} achieved
%%    by the optimization sequence selected by iterative compilation. On the left is the average over the \FIXME{50} inputs, on the right the
%%    average over all 1,000 inputs. The selected sequence works great for the inputs we used, but it fails miserably for the rest, slowing
%%    down the benchmark by \FIXME{5\%} on average. 
%%
%%    The blue bars, on the other hand, show the ideal case where good optimizations are selected based on their average effect on all
%%    inputs, not just a subset. Not only is the average speedup over all 1,000 inputs considerable, \FIXME{13\%} over \texttt{-O3}, but it
%%    also works well for the \FIXME{50} input subset. The speedup for the subset is only \FIXME{1\%} less of what we got when we optimized
%%    specifically for that subset.
%%
%%    Making iterative compilation work in this example is not a matter of handling input sensitivity, we were able to find an optimization
%%    sequence that works well both on average and under most inputs. It is a matter of finding a set of inputs that represents the full
%%    range of inputs the application is likely to process. If we do, we can improve average performance by \FIXME{13\%}. If not, we might
%%    hurt average performance instead.

@@

    %\paragraph{Using real inputs online is not enough.} We could overcome these problems by just evaluating optimization sequences online
    %while the application is being used. This gives us live data but creates a new problem. Optimization sequences are compared based on
    %how much faster the program becomes. When all of them are tested against the same inputs, it is just a matter of comparing runtimes.
    %A shorter runtime for processing the same data means a more efficient binary. With live data, we cannot do this, each binary processes
    %whatever the input happens to be. We need another efficiency metric that only requires a single use of an optimized binary with a
    %single input.

    \paragraph{Challenges of using real inputs online.} We could overcome the problems of representative inputs by just evaluating
    optimization sequences online while the application is being used. 
    %Optimization sequences are compared based on how much faster the program becomes.
    This gives us live data but creates a new problems.
    With live data, we cannot just compare runtimes. 
    When all of the optimization sequences are tested against the same inputs, it is just a matter of comparing runtimes.
    A shorter runtime for processing the same data means a more efficient binary.
    With live data, we cannot do this, each binary processes
    whatever the input happens to be. We need another efficiency metric that only requires a single use of an optimized binary with a
    single input.
